%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Engineering Manager} % Job title
    {\href{https://heyjobs.co}{HeyJobs GmbH}} % Organization
    {Berlin, Germany} % Location
    {July 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, specified and managed implementation of various software components, systems and infrastructure parts throughout our consumer facing, business facing and internal software components.}
        \item {Managed a team of fullstack engineers, mentored them, facilitated their growth and career progression.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior iOS Developer~~~·~~~Web Developer} % Job title
    {\href{https://heyjobs.co}{HeyJobs GmbH}} % Organization
    {Berlin, Germany} % Location
    {April 2016 - July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed built and maintained foundations for cross platform (iOS and Android) application architecture, which was based on Xamarin, C\#, ReactiveUI and MVVM.}
        \item {Built and maintained continuous delivery mechanisms for mobile applications.}
        \item {Built features for the cross platform mobile application, ruby backend and javascript universal frontend webpage.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior iOS Developer} % Job title
    {\href{https://memorado.com}{Memorado GmbH}} % Organization
    {Berlin, Germany} % Location
    {June 2015 - April 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to various features of all brain training applications.}
        \item {Lead the design of application architecture.}
        \item {Developed and maintained continuous delivery systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance iOS Developer} % Job title
    {\href{https://www.adroiti.com}{Adroiti Technologies}} % Organization
    {Santa Monica, CA, USA} % Location
    {September 2015 - October 2017} % Date(s)
    {
       \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {Developed and maintained an iPad + iBeacon based content delivery system for various events and conferences.}
         \item {Developed methods of triangulating distance between iPad stands and visitors in order to accumulate relevant event analytics.}
         \item {Implemented application distribution, automated testing processes and general developer process for multiple teams centered around iOS products.}
       \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder~~~·~~~Developer} % Job title
    {\href{https://delanoir.com}{delanoir}} % Organization
    {Kaunas, Lithuania} % Location
    {December 2012 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a secure file storage application that uses AES256 encryption and scrypt for key generation - \href{http://appstore.com/seenc}{seenc}. It was the first consumer targeted file encryption solution that used scrypt instead of the more popular (and less secure) PBKDF2.}
        \item {Developed an open source tool to ease iOS application build and distribution - \href{http://github.com/carlossless/tangerine}{Tangerine}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {iOS Developer} % Job title
    {\href{https://devbridge.com}{Devbridge Group}} % Organization
    {Kaunas, Lithuania / Chicago, IL, USA} % Location
    {April 2012 - June 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built multiple iOS applications mostly for specific enterprise needs and internal company usage.}
        \item {Developed and maintained continuous integration systems specifically for iOS application delivery and testing.}
        \item {Developed several tools to help with internal and external application distribution.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Part Time~~~·~~~Web Developer} % Job title
    {\href{https://devbridge.com}{Devbridge Group}} % Organization
    {Kaunas, Lithuania / Chicago, IL, USA} % Location
    {July 2009 - May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built multiple web applications mostly based on ASP.NET, C\# and VB.NET ranging from small scale content oriented websites to large scale enterprise web systems.}
        \item {Contributed to building an internal continuous integration scheme.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
